Agenda diversity and coverage bias: A quantitative approach to the agenda-setting theory

### 2018-07-11 paper_balen.tex
Varias correcciones hechas

\par A time-dependent representation is obtained by defining the temporal profile of the topic $i$, $W_i(day)$, by eq.\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, and $h_{ji}$ is the degree of membership of document $j$ on topic $i$. Providing by the fact that each document's vector can have all non-zero components, it is allowed that a document contributes to more than one topics' weight.
In order to reduce noise, we apply a linear filter with a sliding window of size 3, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space which evolves over time. This last normalization prevent us against the differences in the number of articles that each newspaper publishes.

@@

\par A point above the upper inner fence considered a mild outlier and a point aove an outer fence is considered an extreme outlier. The same holds for the lower fences. \footnote{http://www.itl.nist.gov/div898/handbook/prc/section1/prc16.htm}

\subsection{Jensen-Shannon divergence}

\par In probability theory and statistics, the Jensen-Shannon divergence is a method to measure the similarity between two probability distributions. It is based on the Kulback-Leibler divergence  ($D_{KL}$)\ref{eq:jensen_shannon_distance}, but have also useful properties such as it is symmetric and it is always a finite value. The square root of the Jensen-Shannon divergence \ref{eq:jensen_shannon_distance} is a metric often referred to as Jensen-Shannon distance \cite{fuglede2004jensen}.

\begin{equation}
\begin{split}
D_{KL}(P||Q) = -\sum{P(i) log(\frac{Q(i)}{P(i)})} \\
\text{JS Divergence}(P||Q) = \frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] \\
\text{JS Distance (JSD)} = \sqrt(\text{JS Divergence})
\end{split}
\label{eq:jensen_shannon_distance}
\end{equation}

@@

\par The normalized Shannon's entropy \ref{eq:shannon_entropy} as a way to measure how spread is a distribution, taking the maximum value where all outcomes are equally probable in the case of a discrete distribution.

@@

\par The starting point of our analysis is the decomposition of the corpus in ten topics. This is an arbitrary decision, validated in some manner by our knowledge of the corpus, which could be revised in future works.  From the initial ten topics, three of them could be interpreted as part of the same macro-topic called \emph{Elections}. The same happen with two others which we classified as part of the macro-topic called \emph{Missing person}, leaving the  final description of the agendas is made with seven topics. The meaning of the topics or macro-topics are contextualized  in section \ref{sec:Context} of Supplementary Material.

After the procedure described in previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, and all their derivations, as time-dependent distributions.

@@

\par In figure \ref{fig:all_agenda} we show the time evolution of the topics with a bump chart of the Agendas. The bump chart provides  a very useful visualization tool for displaying the relative weight of the topics at the same time that their ranking. In figure \ref{fig:all_agenda} we also highlight some important events related to the dynamics of the topics. \footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving the at least at we can the most important keywords. The queries employed by topic were: \\
Elections: elecciones + cambiemos + kirchner + massa + randazzo \\
Missing person: maldonado + otranto + gendarmeria + desaparicion \\
Former Planning minister: vido + desafuero + minnicelli + baratta \\
Current President: macri + cgt + laboral +  triaca \\
Social leader:  sala + cidh + tupac + amaru + pullen + llermanos + morales \\
Prosecutor’s death: nisman + amia + memorandum + timerman +  bonadio \\
Former Vice-President:  boudou + ciccone +  lijo + vandenbroele + carmona
}

% Wordclouds
\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig1.pdf}
\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw). 
Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic. In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_all_correlation}) and therefore in our construction of the Public Agenda.}
\label{fig:topics_wordclouds}
\end{figure}

% Global Agenda figure!!!
\begin{figure}[h]
\includegraphics[width = \textwidth]{images/Fig2.pdf}
\caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}. The curves width and their ordering are related to the topics relative weight. Some important events related to the topics are pointed out:
\textbf{A}: First news about Santiago Maldonado's disappearance;
\textbf{B}: Primary elections;
\textbf{C}: March one month after Santiago Maldonado's disappearance;
\textbf{D}: March two months after Santiago Maldonado's disappearance;
\textbf{E}: Appearance of Santiago Maldonado's body;
\textbf{F}: General elections;
\textbf{G}: Julio De Vido's detention;
\textbf{H}: Debates on labor reform;
\textbf{I}: Amado Boudou's detention.
A more detailed explanation is given in section \ref{sec:Context}.}
\label{fig:all_agenda}
\end{figure}

@@

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{lp{10cm}}
\toprule
Topic's name & Google Trends query \\ 
\midrule
Elections & elecciones + cambiemos + cristina kirchner + massa + randazzo \\
Missing person & santiago maldonado + juez otranto + patricia bullrich + gendarmería + desaparición forzada \\
Former Planning minister & de vido + desafuero + ministro de planificación + minnicelli + baratta \\
Current President & mauricio macri + cgt + reforma laboral + peña + triaca \\
Social leader & milagro sala + cidh + tupac amaru + pullen llermanos + morales \\
Prosecutor's death & nisman + amia + memorándum con irán + timerman + juez bonadio \\
Former Vice-President & amado boudou + ciccone + ariel lijo + vandenbroele + núñez carmona \\
\bottomrule
\end{tabular}}
\caption{Queries used in Google Trends in order to build the Public Agenda.}
\label{table:gt_queries}
\end{table}

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{lccc}
\toprule
Topic's name & Correlation MA and GT & MA and Twitter & GT and Twitter \\ 
\midrule
Elections & \textbf{0.81} & \textbf{0.59} & \textbf{0.75} \\
Missing person & \textbf{0.68} & \textbf{0.76} & \textbf{0.89} \\
Former Planning minister & \textbf{0.92} & \textbf{0.82} & \textbf{0.87} \\
Current President & \textbf{0.77} & \textbf{0.75} & \textbf{0.63} \\
Social leader & \textbf{0.49} & \textbf{0.25(*)} & \textbf{0.57} \\
Prosecutor's death & \textbf{0.56} & \textbf{0.59} & \textbf{0.75} \\
Former Vice-President & \textbf{0.90} & \textbf{0.92} & \textbf{0.97}\\
\bottomrule
\end{tabular}}
\caption{Correlation between the topics' temporal profiles of the Public Agenda and their counterpart in Media Agenda.
All correlation values are statistical significant ($p < 10^{-9}$), except (*) which is significant with $p < 0.05$.}
\label{table:gt_all_correlation}
\end{table}

\par The figures introduced above show not only the topics and their differences between Agendas, but also the dynamics of the topics.  For instance, we can see in the radar plot of figure \ref{fig:topics_wordclouds}, a greater interest of the audience in the topic \emph{Missing person} than the Media, or inversely in the topic \emph{Prosecutor's death}, at least in the analyzed time-lapse. 
We can also observe a great similarity between \textbf{GT} and \textbf{Tw} agendas which both are different faces of the Public Agenda.

@@

\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media.
In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see that two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections} and coincide with the primary and general legislative elections that took place in August 13th and October 22th. 
In all the agendas these points where detected as outliers except point (d) in Twitter Agenda. Why is that? The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President} which could be decreasing the important this topic.
Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
On the other hand, we focused in point (b), despite not being detected as a outlier, because it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of Santiago Maldonado (see section \ref{sec:Context}). It is important to notice that, the Shannon's Entropy of GT Agenda displays a minimum (collapsing agenda) not shown neither in the Media nor in the Twitter Agendas.
We emphasize the discussion about this topic because we can appreciate  interesting facts that appear along the analysis.

\begin{figure}[h]
\centering
\includegraphics[height=0.75\textheight]{images/Fig3.pdf}
\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure. The horizontal lines are the lower inner fences of each signal in order to identify outliers. The related radar plots shows that those dates when the agenda has a low diversity, the most important topic catches the most public’s attention. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:shannon_entropy_agendas}
\end{figure}

\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
Specifically $H_{Gt} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.

@@

\par Given our interpretation of  the Agendas and time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance. In this context, outliers in selected dates will correspond to divergences between Public and Media Agenda, i.e., specific events where the public interest do not match with media offer.
In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Publics Agendas as a function of time. We focus in three points that seems to be relevant enough. In all cases, the topic distributions at that particular dates displayed by  the radar plots shows that a greater distance is associated with a more interest of public in the topic \emph{Missing person}. 
\par Points \textbf{(c)} and \textbf{(d)} shows that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted  of another way of see  the diversity effect discussed in the last section.

\par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)} seem to show an interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.  In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both \textbf{GT} and \textbf{Tw}) days before that  it happen in the Media Agenda. It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of Santiago Maldonado ("The missing person") that took place on  August 26th. It was very important and and was initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).

@@

\begin{figure}[h]
\centering
\includegraphics[height = 0.75\textheight]{images/Fig4.pdf}
\caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out). The larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which leads to lesser interest in the other topics, which the Media has to cover, maybe except in points (a) and (b) where the Media seems not to anticipate the public interest in the mentioned topic. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:jensen_shannon_gt}
\end{figure}

@@

\par In this section we leave aside the Public Agenda as a whole and we study how the Media agenda of each media outlet. 
In figure \ref{fig:news_agenda} we show the bump charts corresponding to each newspaper analogously to figure \ref{fig:all_agenda}.
The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topics' weights,  the articles are discriminated by newspaper. 
We also show the radar plots showing the average distribution, as made in figure \ref{fig:topics_wordclouds}. 
\par In figure \ref{fig:news_agenda} we can see in a qualitative way the slightly differences between the newspapers' agendas.
For instance, we can see how newspaper called \emph{Pagina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.

% Jensen shannon distance of Dynamic way
\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig5.pdf}
\caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas. For instance, the greater interest of \emph{Pagina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
\label{fig:news_agenda}
\end{figure}

@@

\par In other to detect outliers behavior of a given newspaper respect to the others, we again calculate the Jensen-Shannon distance between the newspapers agenda and the Media Agenda.
Note that this is the distance between the distributions of figure \ref{fig:news_agenda} and the top panel of figure \ref{fig:all_agenda}.
\par In figure \ref{fig:jensen_shannon_news} we show the Jensen-Shannon distance as a function of time.
We detect three points as outliers, although we discard the point \textbf{(b)} due to the low information of \emph{Infobae} in that period. 
The other two points corresponds to differences between \emph{Pagina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.

\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{Pagina 12} before the primary elections, and in point \textbf{(c)} to  the two months rally after the disappearance took place (see section \ref{sec:Context}). Another difference in point \textbf{(c)} corresponds to a greater coverage of \emph{Pagina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.

% Jensen shannon distance of Dynamic way
\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig6.pdf}
\caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}. \emph{Pagina 12} shows the more different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics as can be seen in the radar plots which belongs to points (a) and (c). The anomalous behavior of \emph{Infobae} at pint (b) is due to few articles around that date in our database, therefore we ignore its radar plot. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:jensen_shannon_news}
\end{figure}

@@

\par The greater coverage in the topic \emph{Missing person} by \emph{Pagina 12} is even more clear if we inspect the temporal profile of the topic and compare the coverage given by each newspaper. A difference in the coverage is what it is called \emph{coverage bias} [CITA ACA SEBAS].  In figure \ref{fig:topics_temporal_profiles} we show the temporal profile of the topic \emph{Missing person} (panel (a)) and the topic \emph{Former Planning minister} in panel (b), as an example where the behavior is the opposite, as can be seen below.

\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig7.pdf}
\caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and their corresponding word-clouds of frequent newspapers' keywords}. We interpreted the differences shown in given periods as an indicator of coverage bias. For instance, in figure (a) Pagina 12 pays a greater attention in the first days. In the word-clouds, we show which of the defining words are more frequently used by the corresponding newspaper. Most of them are less informative, but other seems to represent a first approximation in the study of framing.}
\label{fig:topics_temporal_profiles}
\end{figure}

\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{Pagina 12} respect the other newspapers at the beginning of the period. We can, for instance, quantify this difference calculating  the median of the signals. If we focus in the period between July 31th and August 27th, the median of the topic's relative weight for \emph{Pagina 12} is roughly 0.14 and this is statistically significant larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
Analyzing the same period, but in panel (b), we again can show that the median in \emph{Pagina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$)
This quantification is proposed as method of studying coverage bias in the context of the methodology implemented in our work.

>>>>

\par A time-dependent representation is obtained by defining the temporal profile of the topic $i$, $W_i(day)$, by eq.\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$ and $\delta$ is the Kronecker delta. Providing by the fact that each document's vector can have all non-zero components, it is allowed that a document contributes to more than one topics' weight.
In order to reduce noise, we apply a linear filter with a sliding window of size 3, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space which evolves over time. This last normalization prevent us against the differences in the number of articles that each newspaper publishes.

@@

\par A point above the upper inner fence considered a mild outlier and a point above an outer fence is considered an extreme outlier. The same holds for the lower fences \cite{natrella2010nist}.

\subsection{Jensen-Shannon distance}

\par In probability theory and statistics, the Jensen-Shannon divergence ($JS_{Div}$) is a method to measure the similarity between two probability distributions. It is based on the Kullback-Leibler divergence ($D_{KL}$), but have also useful properties such as it is symmetric and it is always a finite value. The square root of the Jensen-Shannon divergence (see eq.\ref{eq:jensen_shannon_distance}, where $M = \frac{P + Q}{2}$) is a metric \cite{fuglede2004jensen} often referred as Jensen-Shannon distance ($JSD$).

\begin{equation}
\begin{split}
D_{KL}(P||Q) = -\sum{P(i) log(\frac{Q(i)}{P(i)})} \\
JSD(P,Q) = \sqrt{JS_{Div}(P,Q)} = \sqrt{\frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] } \\
\end{split}
\label{eq:jensen_shannon_distance}
\end{equation}

@@

\par The normalized Shannon's entropy (eq.\ref{eq:shannon_entropy}) is a way to measure how spread is a distribution, taking the maximum value where all outcomes are equally probable in the case of a discrete distribution.

@@

\par The starting point of our analysis is the decomposition of the corpus in ten topics. This is an arbitrary decision, validated in some manner by our knowledge of the corpus, which could be revised in future works.  From the initial ten topics, three of them could be interpreted as part of the same macro-topic called \emph{Elections}. The same happen with two others which we classified as part of the macro-topic called \emph{Missing person}, leaving the  final description of the agendas as made with seven topics. The meaning of the topics or macro-topics is contextualized in section \ref{sec:Context} of Supplementary Material.

\par After the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, and all their derivations, as time-dependent distributions.

@@

\par In figure \ref{fig:all_agenda} we show the time evolution of the topics with a bump chart of the Agendas. The bump chart provides  a very useful visualization tool for displaying the relative weight of the topics at the same time that their ranking. In figure \ref{fig:all_agenda} we also highlight some important events related to the dynamics of the topics. \footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving at least at we can the most important keywords. The queries employed by topic were: \\
Elections: elecciones + cambiemos + kirchner + massa + randazzo \\
Missing person: maldonado + otranto + gendarmeria + desaparicion \\
Former Planning minister: vido + desafuero + minnicelli + baratta \\
Current President: macri + cgt + laboral +  triaca \\
Social leader:  sala + cidh + tupac + amaru + pullen + llermanos + morales \\
Prosecutor’s death: nisman + amia + memorandum + timerman +  bonadio \\
Former Vice-President:  boudou + ciccone +  lijo + vandenbroele + carmona
}

% Wordclouds
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{images/Fig1.pdf}
\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw). 
Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic. In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_queries}) and therefore in our construction of the Public Agenda.}
\label{fig:topics_wordclouds}
\end{figure}

% Global Agenda figure!!!
\begin{figure}[H]
\includegraphics[width = \textwidth]{images/Fig2.pdf}
\caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}. The curves width and their ordering are related to the topics relative weight. Some important events related to the topics are pointed out:
\textbf{A}: First news about Santiago Maldonado's disappearance;
\textbf{B}: Primary elections;
\textbf{C}: March one month after Santiago Maldonado's disappearance;
\textbf{D}: March two months after Santiago Maldonado's disappearance;
\textbf{E}: Appearance of Santiago Maldonado's body;
\textbf{F}: General elections;
\textbf{G}: Julio De Vido's detention;
\textbf{H}: Debates on labor reform;
\textbf{I}: Amado Boudou's detention.
A more detailed explanation is given in section \ref{sec:Context}.}
\label{fig:all_agenda}
\end{figure}

@@

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{lp{10cm}}
\toprule
Topic's name & Google Trends query \\ 
\midrule
Elections & elecciones + cambiemos + cristina kirchner + massa + randazzo \\
Missing person & santiago maldonado + juez otranto + patricia bullrich + gendarmería + desaparici\'on forzada \\
Former Planning minister & de vido + desafuero + ministro de planificaci\'on + minnicelli + baratta \\
Current President & mauricio macri + cgt + reforma laboral + peña + triaca \\
Social leader & milagro sala + cidh + tupac amaru + pullen llermanos + morales \\
Prosecutor's death & nisman + amia + memor\'andum con ir\'an + timerman + juez bonadio \\
Former Vice-President & amado boudou + ciccone + ariel lijo + vandenbroele + núñez carmona \\
\bottomrule
\end{tabular}}
\caption{Queries used in Google Trends in order to build the Public Agenda.}
\label{table:gt_queries}
\end{table}

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{lccc}
\toprule
Topic's name & Correlation MA and GT & MA and Twitter & GT and Twitter \\ 
\midrule
Elections & \textbf{0.81} & \textbf{0.59} & \textbf{0.75} \\
Missing person & \textbf{0.68} & \textbf{0.76} & \textbf{0.89} \\
Former Planning minister & \textbf{0.92} & \textbf{0.82} & \textbf{0.87} \\
Current President & \textbf{0.77} & \textbf{0.75} & \textbf{0.63} \\
Social leader & \textbf{0.49} & \textbf{0.25(*)} & \textbf{0.57} \\
Prosecutor's death & \textbf{0.56} & \textbf{0.59} & \textbf{0.75} \\
Former Vice-President & \textbf{0.90} & \textbf{0.92} & \textbf{0.97}\\
\bottomrule
\end{tabular}}
\caption{Correlation between the topics' temporal profiles of the Public Agenda and their counterpart in Media Agenda.
All correlation values are statistical significant ($p < 10^{-9}$), except (*) which is significant with $p < 0.05$.}
\label{table:gt_all_correlation}
\end{table}

\par The figures introduced above show not only the topics and their differences between the Agendas, but also the dynamics of the topics.  For instance, we can see in the radar plot of figure \ref{fig:topics_wordclouds}, a greater interest of the audience in the topic \emph{Missing person} than the Media, or inversely in the topic \emph{Prosecutor's death}, at least in the analyzed time-lapse. 
We can also observe a great similarity between \textbf{GT} and \textbf{Tw} agendas which both are different faces of the Public Agenda.

@@

\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media.
In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see that two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections} and are related with the primary and general legislative elections that took place in August 13th and October 22th. 
In all the agendas these points where detected as outliers except point (d) in Twitter Agenda. Why is that? The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President} which could be decreasing the important of this topic.
Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
On the other hand, we focused in point (b), despite not being detected as a outlier, because it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of Santiago Maldonado (see section \ref{sec:Context}). It is important to notice that the Shannon's Entropy of GT Agenda displays a minimum (collapsing agenda) not shown neither in the Media nor in the Twitter Agendas.
We emphasize the discussion about this topic because we can appreciate  interesting facts that appear along the analysis.

\begin{figure}[H]
\centering
\includegraphics[height=0.75\textheight]{images/Fig3.pdf}
\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure. The horizontal lines are the lower inner fences of each signal in order to identify outliers. The related radar plots shows that those dates when the agenda has a low diversity, the most important topic catches the most public’s attention. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:shannon_entropy_agendas}
\end{figure}

\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.

@@

\par Given our interpretation of the Agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance. In this context, outliers in selected dates will correspond to divergences between Public and Media Agenda, i.e., specific events where the public interest do not match with media offer.
In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Publics Agendas as a function of time. We focus in three points that seems to be relevant enough. In all cases, the topic distributions at that particular dates displayed by  the radar plots shows that a greater distance is associated with a more interest of public in the topic \emph{Missing person}. 
\par Points \textbf{(c)} and \textbf{(d)} shows that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted  of another way of seeing the diversity effect discussed in the last section.

\par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)} seem to show an interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.  In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both \textbf{GT} and \textbf{Tw}) days before that  it happen in the Media Agenda. It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of Santiago Maldonado ("The missing person") that took place on  August 26th. It was very important and was initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).

@@

\begin{figure}[H]
\centering
\includegraphics[height = 0.75\textheight]{images/Fig4.pdf}
\caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out). The larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which leads to lesser interest in the other topics, which the Media has to cover, maybe except in points (a) and (b) where the Media seems not to anticipate the public interest in the mentioned topic. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:jensen_shannon_gt}
\end{figure}

@@

\par In this section we leave aside the Public Agenda as a whole and we study how the Media agenda of each media outlet. 
In figure \ref{fig:news_agenda} we show the bump charts corresponding to each newspaper analogously to figure \ref{fig:all_agenda}.
The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topics' weights,  the articles are discriminated by newspaper. 
We also show the radar plots showing the average distribution, as made in figure \ref{fig:topics_wordclouds}. 
\par In figure \ref{fig:news_agenda} we can see in a qualitative way the slightly differences between the newspapers' agendas.
For instance, we can see how newspaper called \emph{P\'agina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.

% Jensen shannon distance of Dynamic way
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{images/Fig5.pdf}
\caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas. For instance, the greater interest of \emph{P\'agina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
\label{fig:news_agenda}
\end{figure}

@@

\par In other to detect outliers behavior of a given newspaper respect to the others, we again calculate the Jensen-Shannon distance between the newspapers agenda and the Media Agenda.
Note that this is the distance between the distributions of figure \ref{fig:news_agenda} and the top panel of figure \ref{fig:all_agenda}.
\par In figure \ref{fig:jensen_shannon_news} we show the Jensen-Shannon distance as a function of time.
We detect three points as outliers, although we discard the point \textbf{(b)} due to the low information of \emph{Infobae} in that period. 
The other two points corresponds to differences between \emph{P\'agina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.

\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{P\'agina 12} before the primary elections, and in point \textbf{(c)} to  the two months rally after the disappearance took place (see section \ref{sec:Context}). Another difference in point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.

% Jensen shannon distance of Dynamic way
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{images/Fig6.pdf}
\caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}. \emph{P\'agina 12} shows the more different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics as can be seen in the radar plots which belongs to points (a) and (c). The anomalous behavior of \emph{Infobae} at pint (b) is due to few articles around that date in our database, therefore we ignore its radar plot. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:jensen_shannon_news}
\end{figure}

@@

\par The greater coverage in the topic \emph{Missing person} by \emph{P\'agina 12} is even more clear if we inspect the temporal profile of the topic and compare the coverage given by each newspaper. A difference in the coverage is what it is called \emph{coverage bias} \cite{dallmann2015media}.  In figure \ref{fig:topics_temporal_profiles} we show the temporal profile of the topic \emph{Missing person} (panel (a)) and the topic \emph{Former Planning minister} in panel (b), as an example where the behavior is the opposite, as can be seen below.

\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{images/Fig7.pdf}
\caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and their corresponding word-clouds of frequent newspapers' keywords}. We interpreted the differences shown in given periods as an indicator of coverage bias. For instance, in figure (a) \emph{P\'agina 12} pays a greater attention in the first days. In the word-clouds, we show which of the defining words are more frequently used by the corresponding newspaper. Most of them are less informative, but other seems to represent a first approximation in the study of framing.}
\label{fig:topics_temporal_profiles}
\end{figure}

\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{P\'agina 12} respect the other newspapers at the beginning of the period. We can, for instance, quantify this difference calculating  the median of the signals. If we focus in the period between July 31th and August 27th, the median of the topic's relative weight for \emph{P\'agina 12} is roughly 0.14 and this is statistically significant larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
Analyzing the same period, but in panel (b), we again can show that the median in \emph{P\'agina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$)
This quantification is proposed as method of studying coverage bias in the context of the methodology implemented in our work.

\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show word-clouds of topic's keywords but separating those who are more frequently mentioned by each newspaper, and filtering the words that are common to all and basically define the factual details of the topic.
Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fernandez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
